Influence of Connectivity on Dung Beetle Communities

### 2025-02-25 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
questions for analyses and cleaning up data
tidbits
introduction outline, beetles by species filtered by block and patch

@@

@@

1. **Species Richness:** absolute number? non-parametric estimators?
1. **Species Diversity:** what index should we compare?
1. **Functional Diversity:** Need to assign each species to a functional group: roller, tunneler. dweller, others?

>>>>

INTRODUCTION

@@

- First Paragraph: What is the topic of your introduction and why is it important/interesting/relevant?

What?

Connectivity and fragmentation

understanding how movement corridors effect populations dung beetles

Dispersal ability

Why?

Understanding responses to landscape change allows us to anticipate how environments might change with further disturbance.

Patterns in population distributions might suggest how we can study focal organisms in the future.

Could help understand how interactions may be changing.

- Second Paragraph: What is known about this topic already?

Effects of landscape change are already very well studied, accross different taxa

effects of edge, patch size, and direct habitat loss

using corridors to connect fragmented landscapes is also well studied and for many taxa

dung beetles as a model system for studying movement, functional diversity, and ecosystem health.

dung beetle populations in connected and fragmented habitats

insect declines in fragmented landscapes

studying coprophagous insects

- Third Paragraph: What isn't known about this topic and why might it change how we think/act about the topic?

How corridors directly impact dung beetle communitites

are changes driven by dispersal ability

at our study site we can directly compare patch connectivity and patch shape with fragmented landscapes to obtain a strong idea of what landscape features effect dung beetle collection.

- Fourth Paragraph: Why hasn't this thing been studied/assessed/done before?

other work at the corridor project but we are doing dung beetles instead

- Fifth Paragraph: Literally the words "Here we..."

Here sampled the commmunity of of dung beetles at the SRS Corridor Experiment to test the following prediction:

Species richness, diversity, and functional diversity will be higher in patches connected by a movement corridor than in patches that are unconnected.

@@

1. **Species Richness:** absolute number? non-parametric estimators?
  - Michaelis-Menten
  - choa?
1. **Species Diversity:** what index should we compare?
  - alpha diversity per patch type
  - beta between patch types
  - hill numbers

1. **Functional Diversity:** Need to assign each species to a functional group: roller, tunneler. dweller, others? 
  - habitat preference (forest, pasture, generalist)
